### 2025-08-17 correlation.qmd
20250817 - chunk labels for troubleshooting

```{r}
mod <- stats::aov(
  fantasyPoints ~ height,
  data = player_stats_seasonal)

@@

```{r}
correlation::correlation(
  data = player_stats_seasonal %>% select(height, fantasyPoints),
  method = "distance"
)
```

@@

```{r}
set.seed(52242) # for reproducibility

>>>>

```{r}
#| label: correlation-ratio

mod <- stats::aov(
  fantasyPoints ~ height,
  data = player_stats_seasonal)

@@

```{r}
#| label: distance-correlation

correlation::correlation(
  data = player_stats_seasonal %>% select(draftround, fantasyPoints),
  method = "distance"
)
```

@@

```{r}
#| label: xi-coefficient

set.seed(52242) # for reproducibility
